---
title: |
  | The Varieties of Turkish Nationalism
  | Step 1: Survey Set-Up
output:
  html_document: 
    number_sections: true
    theme: united
---

```{r setup, include=FALSE}
rm(list = ls())
pacman::p_load(tidyverse)
load("survey_dataframe_version1.R")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

Hello there! Welcome to the replication files for Keskintürk and Kuyucu (2023).

This first RMarkdown document prepares the Varieties of Turkish Nationalism Survey for the analyses. See the data in our shared folder.

# Data Wrangling

## Directions

To facilitate interpretation, we are first going to recode all variables such that higher values indicate nationalist/conservative positions.

```{r}

df <- df |>
  mutate_at(
    .vars = c(
      # nationalism variables
      "nat01",
      "nat03",
      "nat04",
      "nat05",
      "nat06",
      "nat07",
      "nat08",
      "nat09",
      "nat10",
      "nat11",
      "nat12",
      "nat13",
      "nat14",
      # opinion variables
      "o_nomuslim",
      "o_refugee1",
      "o_refugee2",
      "o_violence",
      "o_foreigns",
      "o_abroads1",
      "o_abroads2"
    ),
    list(~ case_when(. == 1 ~ 5,
                     . == 2 ~ 4,
                     . == 3 ~ 3,
                     . == 4 ~ 2,
                     . == 5 ~ 1))
  )

```

## Labeling

OK, let's now categorize nationalism variables, so that we can interpret typologies more clearly later.

```{r}

df <- df |>
  rename(
    # part 1: national identification
    natident1 = nat01,
    ## "I define myself, first and foremost, as part of the Turkish nation."
    natident2 = nat02,
    ## "If I could be a citizen of another country, I would easily give up my citizenship."

    # part 2: national pride
    natpride1 = nat03,
    ## "Being part of the Turkish nation makes me proud."
    natpride2 = nat04,
    ## "Turkey's achievements in international competitions make me proud."
    
    # part 3: membership criteria
    natmembr1 = nat05,
    ## "Speaking Turkish is an indispensable condition of being Turkish."
    natmembr2 = nat06,
    ## "Kurds live in Turkey as equal citizens without any discrimination."
    natmembr3 = nat07,
    ## "I define myself first as a "Turk," and then as a citizen of the Republic of Turkey."
    natmembr4 = nat08,
    ## "I doubt the Turkishness of a non-Muslim."
    
    # part 4: national hubris
    nathubrs1 = nat09,
    ## "I consider my own nation superior to all other nations."
    nathubrs2 = nat10,
    ## "The contribution of Turks to world civilization is higher than other nations."
    nathubrs3 = nat11,
    ## "Turkey lags behind due to the interventions of internal and external enemies."
    nathubrs4 = nat13,
    ## "Discussing controversial events (e.g., the Armenians or the Kurdish issue) bothers me."

    # part 5: national culture and politics
    natcultr1 = nat12,
    ## "It is not race or religion that makes us who we are, but Turkish national culture."
    natcultr2 = nat14,
    ## "Every Turkish citizen has to respect the historical heritage of the country."
  )

```

## Normalization

OK, we processed the data. We are now going to create a second version of the data to use in the upcoming scripts. Before saving our dataset, we will normalize certain continuous variables such that we will have a minimum of 0 and a maximum of 1.

```{r}

# helper function
normalize <- function(x) {
  (x - min(x)) / (max(x) - min(x))
}

# normalize

df <- df |>
  mutate_at(c(
    "age",
    "educ",
    "religiosity",
    "lifestyle",
    "ideology",
    "polint",
    "polinfo",
    "o_ethnomar",
    "o_educlang",
    "o_nomuslim",
    "o_refugee1",
    "o_refugee2",
    "o_violence",
    "o_foreigns",
    "o_abroads1",
    "o_abroads2"
  ), ~(normalize(.) |> as.vector()))

```

# Saving the Dataset

```{r}

save(df, file = "survey_dataframe_version2.R")

```

Proceed with the Step 2: Latent Class Analyses.
