---
title: |
  | The Varieties of Turkish Nationalism
  | Step 3: Resource Allocation Tasks
output:
  html_document: 
    number_sections: false
    theme: united
---

```{r setup, include=FALSE}
rm(list = ls())
pacman::p_load(
  tidyverse, broom, broom.mixed, brms, sjPlot, dagitty, hrbrthemes, knitr)
load("survey_dataframe_version3.R")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
knitr::opts_chunk$set(fig.align = "center")
```

This RMarkdown file uses LCA fits to ask to what extent different nationalism typologies influence resource allocation decisions.

# The Causal Model

Let's draw the proposed model.

```{r, fig.width = 6, fig.height = 4, dpi = 500}

dag.model <- dagitty("dag{
                          I_1 -> Class
                          I_2 -> Class
                          I_3 -> Class
                          .. -> Class
                          I_N -> Class
                          Class -> Treatment
                          Class -> Classification -> Treatment
                          Z_i -> Class
                          Z_i -> Treatment}")
coordinates(dag.model) <-
  list(x = c(I_1 = 0, I_2 = 1, I_3 = 2, .. = 3, I_N = 4, Class = 2, Treatment = 6, Z_i = 5, Classification = 5),
       y = c(I_1 = 3, I_2 = 3, I_3 = 3, .. = 3, I_N = 3, Class = 1, Treatment = 1, Z_i = 2, Classification = 0))
rethinking::drawdag(dag.model, goodarrow = T)

```

# The Description of the Allocation Decisions

Let us first look at the distribution of allocation decisions across four tasks in the sample.

```{r, fig.width = 7.5, fig.height = 5, dpi = 500}

df |>
  dplyr::select(alloc_family, alloc_friend, alloc_ethnic, alloc_anyone) |>
  pivot_longer(cols = everything(),
               names_to = "tasks",
               values_to = "decisions") |>
  mutate(
    tasks = case_when(
      tasks == "alloc_family" ~ "Family",
      tasks == "alloc_friend" ~ "Friend",
      tasks == "alloc_ethnic" ~ "Ethnic Fellow",
      tasks == "alloc_anyone" ~ "Someone from Turkey"
    ),
    tasks = factor(
      tasks,
      levels = c("Ethnic Fellow", "Someone from Turkey", "Family", "Friend")
    )
  ) |>
  ggplot(aes(x = decisions)) +
  geom_density(col = "gray20", fill = "#B7C4CF", alpha = 0.5) +
  theme_ipsum_rc() +
  theme(aspect.ratio = 0.75) +
  labs(x = "Allocation Decisions", y = "Density") +
  facet_wrap( ~ tasks, nrow = 2) +
  scale_y_continuous(
    limits = c(0, 0.06),
    breaks = c(0, 0.05),
    labels = c(0, 0.05)
  )

```

# Testing Ingroup Resource Allocation

We conducted an allocation task along four dimensions, all set against an individual *anywhere in the world*: (a) someone with the same ethnicity, (b) someone who lives in Turkey, (c) someone from your family, and (d) someone from your friendship circle.

While (a) and (b) tries to capture national categorization, (c) and (d) tries to set-up a baseline for familiar ingroups.

Before fitting the models, let's standardize our allocation decisions so that we can easily fit the Bayesian regressions below.

```{r}

df <- df |> 
  mutate(
    alloc_ethnic = (alloc_ethnic - mean(alloc_ethnic)) / sd(alloc_ethnic),
    alloc_anyone = (alloc_anyone - mean(alloc_anyone)) / sd(alloc_anyone),
    alloc_family = (alloc_family - mean(alloc_family)) / sd(alloc_family),
    alloc_friend = (alloc_friend - mean(alloc_friend)) / sd(alloc_friend),
  )

```

## Bayesian Model Fits

Let's first fit four regression models for each of the decision.

```{r}

# model fits

m1 <- brm(
  alloc_ethnic ~
    class +
    party + ideology + relig + religiosity +
    gender + age + ethnic + educ,
  data = df,
  seed = 11235,
  silent = 2,
  refresh = 0
)

m2 <- brm(
  alloc_anyone ~
    class +
    party + ideology + relig + religiosity +
    gender + age + ethnic + educ,  
  data = df,
  seed = 11235,
  silent = 2,
  refresh = 0
)

m3 <- brm(
  alloc_family ~
    class +
    party + ideology + relig + religiosity +
    gender + age + ethnic + educ,
  data = df,
  seed = 11235,
  silent = 2,
  refresh = 0
)

m4 <- brm(
  alloc_friend ~
    class +
    party + ideology + relig + religiosity +
    gender + age + ethnic + educ,
  data = df,
  seed = 11235,
  silent = 2,
  refresh = 0
)

# collect and tidy the models

model_univ <- list(m1,
                   m2, 
                   m3, 
                   m4)
model_univ <-
  map(model_univ,
      broom.mixed::tidyMCMC,
      conf.int = T,
      conf.level = 0.89)

```

## Plotting the Coefficient Values

```{r, fig.width = 8, fig.height = 6}

# step 1
model_univ <- bind_rows(model_univ, .id = "depvar") |>
  filter(term == "b_classCreedal" | term == "b_classDisengaged" | term == "b_classModerate")

# step 2
model_univ <- model_univ |>
  mutate(
    term = factor(
      term, 
      levels = c(
        "b_classCreedal", "b_classDisengaged", "b_classModerate"),
      labels = c(
        "Creedal", "Disengaged", "Moderate"
      )),
    depvar = case_when(
      depvar == 1 ~ "Ethnic Fellow",
      depvar == 2 ~ "Someone from Turkey",
      depvar == 3 ~ "Family",
      depvar == 4 ~ "Friend"
    ),
    depvar = factor(depvar, levels = c(
      "Ethnic Fellow", "Someone from Turkey", "Family", "Friend"
    ))
  )

# step 3
model_univ |>
  ggplot(
    aes(x = term, y = estimate)) + 
  geom_point() + 
  geom_linerange(aes(ymin = conf.low, ymax = conf.high)) + 
  facet_wrap(~ depvar, nrow = 2) + 
  theme_ipsum_rc(grid = 'Y') + 
  labs(x = "Classes", y = "Δ in Average Allocation to Strangers") +
  geom_hline(yintercept = 0)

# print-out
kable(model_univ, align = "c")

```

Proceed with the Step 4: Opinion Correlations.
