---
title: |
  | The Varieties of Turkish Nationalism
  | Step 4: Opinion Correlations
output:
  html_document: 
    number_sections: false
    theme: united
---

```{r setup, include=FALSE}
rm(list = ls())
pacman::p_load(
  tidyverse, ggeffects, broom, hrbrthemes, gridExtra)
load("survey_dataframe_version3.R")
knitr::opts_chunk$set(dpi = 500)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

This RMarkdown file uses latent classes as predictors for a variety of opinions. Unlike the previous section, we will use base `lm` functions to fit the regressions for fast replication, though the determined replicator can switch to `brms` versions. The results are largely same

# Model Fits for Beliefs

We have 9 belief items. Let's fit OLS models for each of them.

```{r}

model_pols <- lapply(df[,
                        c(
                          "o_ethnomar",
                          "o_educlang",
                          "o_nomuslim",
                          "o_refugee1",
                          "o_refugee2",
                          "o_violence",
                          "o_foreigns",
                          "o_abroads1",
                          "o_abroads2"
                        )],
                     function(x)
                       lm(
                         x ~
                           class +
                           gender + ethnic + age + educ + relig + religiosity + lifestyle +
                           party + ideology + polint + polinfo,
                         data = df
                       ))

```

# Marginal Mean Values for Each Class

```{r, fig.width = 12.5, fig.height= 10}

p1 <-
  plot(ggemmeans(
    model_pols[[1]], 
    "class [all]", 
    ci.level = 0.89,
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.25, .75),
    breaks = c(.25, .35, .45, .55, .65, .75)) + 
  labs(x = "", y = "Predicted Value", title = "Inter-Ethnic Marriage") +
  theme_ipsum_rc()

p2 <-
  plot(ggemmeans(
    model_pols[[2]], 
    "class [all]", 
    ci.level = 0.89,
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.10, .60),
    breaks = c(.10, .20, .30, .40, .50, .60)) + 
  labs(x = "", y = "", title = "Language of Education") +
  theme_ipsum_rc()

p3 <-
  plot(ggemmeans(
    model_pols[[3]], 
    "class [all]", 
    ci.level = 0.89,
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.20, .70),
    breaks = c(.20, .30, .40, .50, .60, .70)) + 
  labs(x = "", y = "", title = "Trust in Non-Muslims") +
  theme_ipsum_rc()

p4 <-
  plot(ggemmeans(
    model_pols[[4]], 
    "class [all]", 
    ci.level = 0.89,
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.50, 1),
    breaks = c(.50, .60, .70, .80, .90, 1)) + 
  labs(x = "", y = "Predicted Value", title = "Citizenship to Immigrants") +
  theme_ipsum_rc()

p5 <-
  plot(ggemmeans(
    model_pols[[5]], 
    "class [all]", 
    ci.level = 0.89,
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.50, 1),
    breaks = c(.50, .60, .70, .80, .90, 1)) + 
  labs(x = "", y = "", title = "State Favoring Turks") +
  theme_ipsum_rc()

p6 <-
  plot(ggemmeans(
    model_pols[[6]], 
    ci.level = 0.89,
    "class [all]", 
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.25, .75),
    breaks = c(.25, .35, .45, .55, .65, .75)) + 
  labs(x = "", y = "", title = "State Violence") +
  theme_ipsum_rc()

p7 <-
  plot(ggemmeans(
    model_pols[[7]], 
    ci.level = 0.89,
    "class [all]", 
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.25, .75),
    breaks = c(.25, .35, .45, .55, .65, .75)) + 
  labs(x = "Class", y = "Predicted Value", title = "Trust in Foreigners") +
  theme_ipsum_rc()

p8 <-
  plot(ggemmeans(
    model_pols[[8]], 
    ci.level = 0.89,
    "class [all]", 
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.25, .75),
    breaks = c(.25, .35, .45, .55, .65, .75)) + 
  labs(x = "Class", y = "", title = "Army Abroad") +
  theme_ipsum_rc()

p9 <-
  plot(ggemmeans(
    model_pols[[9]], 
    ci.level = 0.89,
    "class [all]", 
    vcov.fun = "vcovCL"),
    ci.style = "dot",
    limits = c(.25, .75),
    breaks = c(.25, .35, .45, .55, .65, .75)) + 
  labs(x = "Class", y = "", title = "Turks Abroad") +
  theme_ipsum_rc()

gridExtra::grid.arrange(
  p1, p2, p3, p4, p5, p6, p7, p8, p9, nrow = 3
)

```
